Numerical Solution of Point Defect Equations by MOOSE

### 2021-01-11 examples/point_defects/article/article.tex
article-edit

  Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable. Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE as bencmark problem, and its results are compared to analytical results for validation.

  In this approach, unlike the simulations in this study, the mutual recombination term in Eq. \ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for spherical grain of radius \textit{a} are found as below.\cite{heald1977}\\

@@

  As seen in Fig. \ref{figure:concentrations_MOOSE_analytical}, MOOSE results exactly match with the analytical solution, which makes it a useful tool to analyze behavior of defect concentrations.
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=0.55]{concentration_profiles_MOOSE_Analytical_Neutron_0}
    \caption{Comparison of MOOSE results with analytical solution for spherical grain.}
    \label{figure:concentrations_MOOSE_analytical}
  \end{figure}
  \newpage
  \subsubsection{Concentrations} \hspace{10pt}
  The defect concentrations can follow different patterns depending on their properties. Interstitials diffuse through sinks faster than vacancies, so their steady state concentrations becomes lower (see Fig. \ref{figure:average_concentrations_neutron_5}). The effect of grain size and dose rate are shown in the same figure. As seen, grain size could change the entire behavior of average defect concentration, while dose rate changes the gap between defect concentrations.

    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_neutron_5_size}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a)low neutron dose rate, b) high neutron dose rate}
      \label{figure:average_concentrations_neutron_5}
    \end{figure}

@@

    For unbiased case, as a result of uniform defect production and equilibrium condition at boundaries, the concentration profiles are symmetrical around domain center. The steady state concentration at center doesn't change significantly with increasing size as shown in Fig. \ref{figure:concentrations_neutron_0_1e-6}. In case of high neutron dose rate, concentration levels increase, profiles become more stable (see Fig. \ref{figure:concentrations_neutron_0_1e-3}).\\

    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
      \caption{Concentration profiles for low neutron dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_0_1e-6}
    \end{figure}
    \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
      \caption{Concentration profiles for high neutron dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_0_1e-3}
    \end{figure}
    \newpage
     If production bias (\%5) is applied, the steady state concentration profiles change considerably. The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig. \ref{figure:concentrations_neutron_5_1e-6}a). Moreover, the depth of profile gets larger with increasing grain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary. The vacancy concentration, on the other hand, increases proportional to grain size, and its profile starts having peak at higher concentrations as seen in Fig. \ref{figure:concentrations_neutron_5_1e-6}b.\\
    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
      \caption{Concentration profiles for low neutron dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_5_1e-6}
    \end{figure}\\

    Similar to unbiased case, average concentration levels increases with dose rate. But, the most important effect of high neutron dose rate is causing the interstitial concentration profile to flip in smaller grain sizes than 500 nm (see Fig. \ref{figure:concentrations_neutron_5_1e-3}).\\
    \begin{figure}[htb!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
      \caption{Concentration profiles for high neutron dose rate with 0\% production bias, a) interstitial concentration b) vacancy concentration}
      \label{figure:concentrations_neutron_5_1e-3}
    \end{figure}

@@

    The vacancy supersaturation curves for biased neutron irradation is given in Fig. \ref{figure:vacancy_supersaturation_neutron_5}. Since the defect concentrations have symmetrical profiles for neutron irradation, supersaturation curves are also symmetrical around grain center. The plot shows a non-linear increase in supersaturation values as grain gets larger.
      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-neutron-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
        \caption{Vacancy supersaturation profiles for 5\% production bias, a)low neutron dose rate, b) high neutron dose rate}
        \label{figure:vacancy_supersaturation_neutron_5}
      \end{figure}

@@

  The results of bencmark problem, previously discussed in Fig. \ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations. Table \ref{table:sink_strengths_calculations} show the comparison of calculations.
    \begin{table}[h!]
      \centering
      \caption{Comparison of sink strength calculations}
      \label{table:sink_strengths_calculations}
      \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}||  }
         \hline
          & MOOSE & Analytical\\
         \hline\hline\hline
         ${Z_{gb,i}}$  & 1.257206e-05 m & 1.257332e-05 m\\
         ${Z_{gb,v}}$  & 1.256941e-05 m & 1.257332e-05 m\\
         ${k_{gb,i}}$  & 2.401086e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         ${k_{gb,v}}$  & 2.400580e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         \hline
      \end{tabular}
    \end{table}
    \newpage
    Sink strength plots are presented in Fig. \ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}. The effect of flipping behavior is not visible in the plot of grain boundary sink strength, ${Z^{gb}}$, but there is a significant change on total grain boundary sink strength, ${k^2_i}$ after critical grain size of ${\sim}$1000 nm. In case of high dose rate, the critical grain size drops to ${\sim}$250 nm (Fig. \ref{figure:sink_strengths_neutron_5_1e-6}b).
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
        \label{figure:sink_strengths_neutron_5_1e-6}
      \end{figure}

      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
        \label{figure:sink_strengths_neutron_5_1e-3}
      \end{figure}

      \newpage
      The calculated sink strengths for different production bias and for different grain sizes are presented by a 3D surface plot as given in Fig. \ref{figure:sink_strength_moose_neutron_3D}.
      \begin{figure}[h!]  %Sink Strength 3D - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Zi_scaled}}
        \subfloat{b)\includegraphics[scale=0.5]{sink_strength_moose_neutron_3D_Zv_scaled}}
        \qquad
        \subfloat{c)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_ki_scaled}}
        \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
        \caption{Change of sink strengths with grain size and production bias for low neutron dose rate in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
        \label{figure:sink_strength_moose_neutron_3D}
      \end{figure}

      \begin{figure}[h!]  %GB Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_neutron_Zi_scaled_nolegend}}
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_neutron_Zv_scaled_nolegend}}
        \subfloat{\includegraphics[scale=0.35]{legend}}
        \qquad
        % \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron_500-5000nm}}
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}
        \caption{Change of sink strengths with production bias for low neutron dose rate, a) interstitial GB sink strength, b) vacancy GB sink strength}
        \label{figure:sink_strengths_neutron_bias_Z}
      \end{figure}

      \begin{figure}[h!]  %Total GB Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_neutron_ki_scaled_nolegend}}
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_neutron_kv_scaled_nolegend}}                \subfloat{\includegraphics[scale=0.35]{legend}}
        \qquad
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron_500-5000nm}}
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
        \caption{Change of sink strengths with production bias for low neutron dose rate, a) total interstitial GB sink strength, b) total vacancy GB sink strength}
        \label{figure:sink_strengths_neutron_bias_k}
      \end{figure}

@@

    The vacancy supersaturation curves for ion irradation case are quite similar to ones for neutron irradation case. The only difference is the asymmetrical shape of curves originates from concentration profiles. The non-linear increase in supersaturation values as domain gets larger is observed for ion irradation too.
      \begin{figure}[h!]  %Ion - %5 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
        \caption{Vacancy supersaturation profiles for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
        \label{figure:vacancy_supersaturation_ion_5}
      \end{figure}
      \newpage
    \subsubsection{Sink Strengths} \hspace{10pt}
    The sink strengths are directly related to concentration at center and flow at boundary. The change in centerline defect concentrations are not as considerable as neutron case. So, the flow or flux at boundary becomes more dominant on sink strength profiles (see Fig. \ref{figure:sink_strengths_ion_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}).
      % \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
      %   \centering
      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
      %   \qquad
      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
      %   \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
      %   \label{figure:sink_strengths_ion_0_1e-6}
      % \end{figure}
      \begin{figure}[h!]  %Sink Strength - ion 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_Z_scaled}}
        \qquad
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
        \label{figure:sink_strengths_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
        \label{figure:sink_strengths_ion_5_1e-3}
      \end{figure}

>>>>

  Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable. Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE as benchmark problem, and its results are compared to analytical results for validation.

  In this approach, unlike the simulations in this study, the mutual recombination term in Eq. \ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for a spherical grain of radius \textit{a} are found as below.\cite{heald1977}\\

@@

  This approach is tested in MOOSE by solving point defect concentrations for a spherical grain having radius of 500 nm. As seen in Fig. \ref{figure:concentrations_MOOSE_analytical}, MOOSE results exactly match with the analytical solution, which makes it a useful tool to analyze behavior of defect concentrations.
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=0.55]{concentration_profiles_MOOSE_Analytical_Neutron_0}
    \caption{Comparison of MOOSE results with analytical solution for spherical grain (\textit{a}=500 nm).}
    \label{figure:concentrations_MOOSE_analytical}
  \end{figure}
  \newpage
  \subsubsection{Concentrations} \hspace{10pt}
  The defect concentrations can follow different patterns depending on their properties. Interstitials diffuse to sinks faster than vacancies, so their steady state concentrations becomes lower (see Fig. \ref{figure:average_concentrations_neutron_5}). The effect of grain size and dose rate are shown in the same figure. The effect of grain size on the point defect kinetics resembles to some extent the effect of temperature. This is due to the fact that both factors affect the diffusion kinetics of defects. However, as will be discussed shortly, its effect on the spatial steady-state profiles is even more complex. The dose rate acts like an amplifier and change intensity of the defect behavior, thus the seperation between defect concentrations becomes more explicit.

    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_neutron_5_size}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a)low dose rate neutron, b) high dose rate neutron}
      \label{figure:average_concentrations_neutron_5}
    \end{figure}

@@

    For unbiased case, as a result of uniform defect production and equilibrium condition at boundaries, the concentration profiles are symmetrical around domain center. The steady state concentration at center doesn't change significantly with increasing size as shown in Fig. \ref{figure:concentrations_neutron_0_1e-6}. In case of high dose rate neutron, concentration levels increase at the center of domain with higher gradients close to the boundaries. (see Fig. \ref{figure:concentrations_neutron_0_1e-3}).\\

    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
      \caption{Concentration profiles for low dose rate neutron with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_0_1e-6}
    \end{figure}
    \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
      \caption{Concentration profiles for high dose rate neutron with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_0_1e-3}
    \end{figure}
    \newpage
     If production bias (\%5) is applied, the steady state concentration profiles change considerably. The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig. \ref{figure:concentrations_neutron_5_1e-6}a). Moreover, the depth of profile gets larger with increasing grain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary. The vacancy concentration, on the other hand, increases proportional to grain size, and its profile starts having peak at higher concentrations as seen in Fig. \ref{figure:concentrations_neutron_5_1e-6}b.\\
    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
      \caption{Concentration profiles for low dose rate neutron with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_5_1e-6}
    \end{figure}\\

    Similar to unbiased case, average concentration levels increases with dose rate. But, the most important effect of high dose rate neutron is causing the interstitial concentration profile to flip in smaller grain sizes than 500 nm (see Fig. \ref{figure:concentrations_neutron_5_1e-3}).\\
    \begin{figure}[htb!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
      \caption{Concentration profiles for high dose rate neutron with 0\% production bias, a) interstitial concentration b) vacancy concentration}
      \label{figure:concentrations_neutron_5_1e-3}
    \end{figure}

@@

    The vacancy supersaturation curves for biased neutron irradation is given in Fig. \ref{figure:vacancy_supersaturation_neutron_5}. Since the defect concentrations have symmetrical profiles for neutron irradation, supersaturation curves are also symmetrical around grain center. The plot shows a non-linear increase in supersaturation values as grain gets larger.
      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-neutron-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
        \caption{Vacancy supersaturation profiles for 5\% production bias, a)low dose rate neutron, b) high dose rate neutron}
        \label{figure:vacancy_supersaturation_neutron_5}
      \end{figure}

@@

  The results of bencmark problem, previously discussed in Fig. \ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations. Table \ref{table:sink_strengths_calculations} show the comparison of calculations.
    \begin{table}[h!]
      \centering
      \caption{Comparison of sink strength calculations}
      \label{table:sink_strengths_calculations}
      \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}||  }
         \hline
          & MOOSE & Analytical\\
         \hline\hline\hline
         ${Z_{gb,i}}$  & 1.257206e-05 m & 1.257332e-05 m\\
         ${Z_{gb,v}}$  & 1.256941e-05 m & 1.257332e-05 m\\
         ${k_{gb,i}}$  & 2.401086e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         ${k_{gb,v}}$  & 2.400580e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         \hline
      \end{tabular}
    \end{table}
    \newpage
    Sink strength plots are presented in Fig. \ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}. The effect of flipping behavior is not visible in the plot of grain boundary sink strength, ${Z^{gb}}$, but there is a significant change on total grain boundary sink strength, ${k^2_i}$ after critical grain size of ${\sim}$1000 nm. In case of high dose rate, the critical grain size drops to ${\sim}$250 nm (Fig. \ref{figure:sink_strengths_neutron_5_1e-6}b).
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low dose rate neutron, b) high dose rate neutron}
        \label{figure:sink_strengths_neutron_5_1e-6}
      \end{figure}

      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low dose rate neutron, b) high dose rate neutron}
        \label{figure:sink_strengths_neutron_5_1e-3}
      \end{figure}

      \newpage
      The calculated sink strengths for different production bias and for different grain sizes are presented by a 3D surface plot as given in Fig. \ref{figure:sink_strength_moose_neutron_3D}.
      \begin{figure}[h!]  %Sink Strength 3D - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Zi_scaled}}
        \subfloat{b)\includegraphics[scale=0.5]{sink_strength_moose_neutron_3D_Zv_scaled}}
        \qquad
        \subfloat{c)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_ki_scaled}}
        \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
        \caption{Change of sink strengths with grain size and production bias for low dose rate neutron in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
        \label{figure:sink_strength_moose_neutron_3D}
      \end{figure}

      \begin{figure}[h!]  %GB Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_neutron_Zi_scaled_nolegend}}
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_neutron_Zv_scaled_nolegend}}
        \subfloat{\includegraphics[scale=0.35]{legend}}
        \qquad
        % \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron_500-5000nm}}
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}
        \caption{Change of sink strengths with production bias for low dose rate neutron, a) interstitial GB sink strength, b) vacancy GB sink strength}
        \label{figure:sink_strengths_neutron_bias_Z}
      \end{figure}

      \begin{figure}[h!]  %Total GB Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_neutron_ki_scaled_nolegend}}
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_neutron_kv_scaled_nolegend}}                \subfloat{\includegraphics[scale=0.35]{legend}}
        \qquad
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron_500-5000nm}}
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
        \caption{Change of sink strengths with production bias for low dose rate neutron, a) total interstitial GB sink strength, b) total vacancy GB sink strength}
        \label{figure:sink_strengths_neutron_bias_k}
      \end{figure}

@@

    The vacancy supersaturation curves for ion irradation case are quite similar to ones for neutron irradation case. The only difference is the asymmetrical shape of curves originates from concentration profiles. The non-linear increase in supersaturation values as domain gets larger is observed for ion irradation too.
      \begin{figure}[h!]  %Ion - %5 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
        \caption{Vacancy supersaturation profiles for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
        \label{figure:vacancy_supersaturation_ion_5}
      \end{figure}
      \newpage
    \subsubsection{Sink Strengths} \hspace{10pt}
    The sink strengths are directly related to concentration at center and flow at boundary. The change in centerline defect concentrations are not as considerable as neutron case. So, the flow or flux at boundary becomes more dominant on sink strength profiles (see Fig. \ref{figure:sink_strengths_ion_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}).
      % \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
      %   \centering
      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
      %   \qquad
      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
      %   \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
      %   \label{figure:sink_strengths_ion_0_1e-6}
      % \end{figure}
      \begin{figure}[h!]  %Sink Strength - ion 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_Z_scaled}}
        \qquad
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
        \label{figure:sink_strengths_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low dose rate neutron, b) high dose rate neutron}
        \label{figure:sink_strengths_ion_5_1e-3}
      \end{figure}
